---
title: "Plotly"
author: "Aixa Rodriguez Salan"
date: "27 de septiembre de 2017"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(repos='http://cran.rstudio.com/')
packages<-c("plotly","datasets","ggplot2")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
library(plotly)
library(datasets)
library(ggplot2)
```

##<span style="color:#FC345C"> Instructions </span> 
<font size="4">Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!</font>

<span style="color:#FC345C"> Review Criteria </span> 

<font size="4">The rubric contains the following two questions:

1. Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?
2. Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?</font>

## <span style="color:#FC345C"> Data </span> 

<font size="4">Using dataset ToothGrowth in the R datasets package </font>

```{r data, warning=FALSE, message=FALSE,echo=TRUE}
df<-ToothGrowth
df$pred<-predict(lm(len ~ dose, data = df))
head(df)
```

## <span style="color:#FC345C"> Graph </span> 

```{r graph, warning=FALSE, message=FALSE}
df<-ToothGrowth
df$pred<-predict(lm(len ~ dose, data = df))
ggplotly(ggplot(df,aes(y = len, x = dose)) +  geom_point(aes(color = supp)) +  geom_line(aes(y = pred)) +  geom_smooth())
```

